Hierarchical Dispatching and Overriding

### 2017-06-18 Aplas17/sections/Introduction.tex
local

A reason why programming languages have resisted to multiple
inheritance in the past is that, as Cook~\cite{Cook1987} put it, 
``\emph{multiple inheritance is good but there is no good way to do it}''.
One of the most sensitive and critical issues is perhaps the ambiguity
introduced by multiple inheritance. One case is the famous
\textit{diamond problem}~\cite{Sak89dis,Singh1995} (also known as ``fork-join inheritance''~\cite{Sak89dis}). 
In the diamond problem, inheritance could allow
one feature to be inherited from multiple parent classes that share a
common ancestor, hence
conflicts arise. The variety of strategies for resolving such conflicts
urges the occurrence of different multiple inheritance models,
including traits, mixins, CZ~\cite{malayeri2009cz}, and many others. Existing
languages and research have taken care of this case extensively. Other issues
including how multiple inheritance deals with state, 
have also been discussed quite extensively~\cite{classless,malayeri2009cz,stroustrup1995}.

>>>>

A reason why programming languages have resisted to multiple
inheritance in the past is that, as Cook~\cite{Cook1987} puts it, 
``\emph{multiple inheritance is good but there is no good way to do it}''.
One of the most sensitive and critical issues is perhaps the ambiguity
introduced by multiple inheritance. One case is the famous
\textit{diamond problem}~\cite{Sak89dis,Singh1995} (also known as ``fork-join inheritance''~\cite{Sak89dis}). 
In the diamond problem, inheritance could allow
one feature to be inherited from multiple parent classes that share a
common ancestor, hence
conflicts arise. The variety of strategies for resolving such conflicts
urges the occurrence of different multiple inheritance models,
including traits, mixins, CZ~\cite{malayeri2009cz}, and many others. Existing
languages and research have taken care of this case extensively. Other issues
including how multiple inheritance deals with state, 
have also been discussed quite extensively~\cite{classless,malayeri2009cz,stroustrup1995}.
